---
title: "Lab6"
author: "Nehir Arpat"
date: "2024-10-10"
output: "github_document"
---

# Load Packages
```{r}
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(psych)
library(bruceR)
library(ggsci)
library(see)
library(car)
library(readr)
library(ggstatsplot)
library(performance)
library(sjPlot)
library(emmeans)
```

# Load Datasets
```{r}

dataset <- read_csv("~/Documents/GitHub/Research/Data file Einstein.csv")

```

# Unnecessary Data
```{r}

# Deleting Origin data
dataset <- dataset %>% select(-Origin_0)

# I don't need the origins of participants and because most are Australian, it is marked NA. 
# I can't perform listwise deletion otherwise.

```

# Missing Data
```{r}

#Listwise deletion
list_dataset<- drop_na(dataset)

#pair wise deletion will only be used when you run the actual analysis using "na.rm = TRUE"

```

# Get Summary Descriptive Statistics
```{r}
list_dataset %>% 
  group_by(Gender_0) %>%
  dplyr::summarize(mean_SCAS    = mean(SCAS_TOTAL_0),
      mean_SCS    = mean(SCS_Total_0),
      std_dev_SCAS = sd(SCAS_TOTAL_0),
      std_dev_SCs = sd(SCS_Total_0),
      corr_SCAS_  = cor(SCAS_TOTAL_0, SCS_Total_0)
    )

```


# Normality for Anxiety Scores
```{r}

ggplot(list_dataset, aes(x = SCAS_TOTAL_0)) + geom_histogram(binwidth = 2) + theme_classic()

ggplot(list_dataset, aes(x = SCAS_TOTAL_0)) + geom_density(adjust = 2)  + theme_classic()

qq<-ggplot(list_dataset, aes(sample = SCAS_TOTAL_0)) + geom_qq()  + theme_classic()

qq+ geom_qq_line()


#functions below are base R functions, they can do the job, but not as customizable as ggplot

hist(list_dataset$SCAS_TOTAL_0)

qqnorm(list_dataset$SCAS_TOTAL_0, col = "steelblue", lwd = 2)

plot(density(list_dataset$SCAS_TOTAL_0, na.rm = TRUE, bw = 90),  lwd=2, main = "")

describe(list_dataset$SCAS_TOTAL_0)

shapiro.test(list_dataset$SCAS_TOTAL_0)

```
# Normality for Self-Compassion Scores
```{r}

ggplot(list_dataset, aes(x = SCS_Total_0)) + geom_histogram(binwidth = .8) + theme_classic()

ggplot(list_dataset, aes(x = SCS_Total_0)) + geom_density(adjust = 2)  + theme_classic()

qq<-ggplot(list_dataset, aes(sample = SCS_Total_0)) + geom_qq()  + theme_classic()

qq+ geom_qq_line()


#functions below are base R functions, they can do the job, but not as customizable as ggplot

hist(list_dataset$SCS_Total_0)

qqnorm(list_dataset$SCS_Total_0, col = "steelblue", lwd = 2)

plot(density(list_dataset$SCS_Total_0, na.rm = TRUE, bw = 90),  lwd=2, main = "")

describe(list_dataset$SCS_Total_0)

shapiro.test(list_dataset$SCS_Total_0)
```

#Regression for Gender 
```{r}
model <- lm(SCAS_TOTAL_0 ~ Gender_0 + SCS_Total_0, data = list_dataset)
check_model(model)
model_summary(model)
tab_model(model)

plot_model(model,  type ="est",  show.values = TRUE, vline.color = "#1B191999", line.size = 1.5, dot.size = 2.5, colors = "blue") + theme_bruce()
```

# I decided to use a subscale rather than the whole scale. I will fix the other parts accordingly later on bc I have to submit this by tonight.

#Reliability for Generalized Anxiety Subscale
```{r}

bruceR::Alpha(list_dataset, vars=c("SCAS_1_0", "SCAS_3_0", "SCAS_4_0", "SCAS_20_0", "SCAS_22_0", "SCAS_24_0"))
```

#Reliability for Self-Compassion Subscale
```{r}
bruceR::Alpha(list_dataset, vars=c("SCS_2_0", "SCS_3_0", "SCS_5_0", "SCS_6_0", 
  "SCS_7_0", "SCS_10_0"))
```

# Exploratory Factor Analysis for Generalized Anxiety Subscale
```{r}
#In factor analysis, using reverse scored items or not does not make a difference in interpretation. If you use unrecoded items, it will just make the loadings negative

EFA(list_dataset, vars=c("SCAS_1_0", "SCAS_3_0", "SCAS_4_0", "SCAS_20_0", "SCAS_22_0", "SCAS_24_0"), method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
```


# Exploratory Factor Analysis for Self-Compassion Subscale
```{r}
EFA(list_dataset, vars=c("SCS_2_0", "SCS_3_0", "SCS_5_0", "SCS_6_0", 
  "SCS_7_0", "SCS_10_0"), method = "pa", plot.scree = TRUE, nfactors = c("parallel"))
```

